`phyr`: An R package for phylogenetic species-distribution modelling in ecological communities

### 2019-09-20 ms.Rmd
update closing remarks [skip ci]

The model formula of `pglmm()` is general and can be applied to other tools to fit phylogenetic species-distribution models. In the future, we plan to develop interfaces to fit such models with more bayesian programs such as Stan (based on the R package `brm`) [@brmsR2018]. It is our hope that the `phyr` package and the proposed model formula for phylogenetic species-distribution models will facilitate the usage of such models by other researchers.

>>>>

The model formula of `pglmm()` is general and can be applied using other tools to fit phylogenetic species-distribution models. Thus, `pglmm()` can serve the developer community as a shell for new methods that fit GLMMs, with `phyr` providing an easy user interface. We hope that the `phyr` package will help current and future researchers formulate and analyze phylogenetic species-distribution models.
